---
title: "Swiggy Whole"
author: "Team S"
date: "2022-10-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Loading the dataset

```{r}
print(getwd())
df=read.csv(file ="Swiggy_dataset.csv")
```


## Data Structure

```{r}
head(df)
```


```{r}
dim(df)
```

```{r}
str(df)
```

```{r}
summary(df)
```

## Data Cleaning and Imputation

### Removing Records having NA values
```{r}
df=df[-18]
dim(df)
str(df)
```



```{r}
df=df[complete.cases(df),]
dim(df)
```

```{r}
#install.packages("Hmisc")
library(ggplot2)
library(Hmisc)
```

### Deriving cost from string type
```{r}
cost=c()
for(i in df$costForTwoStrings){
  s=substr(i,4,6)
  cost=c(cost,as.integer(s))
}

df$costForTwoStrings =cost
cost=df[complete.cases(df),]
#cost$costForTwoStrings
dim(cost)
```


## Data Analysis

### 1. Average Cost for 2 in all cities
```{r}
library(dplyr)
cities=c("Chennai   ","Mumbai    ","Hyderabad ","Ahmedabad ","Bangalore ","Surat     ","Kolkata   ","Pune      ","Delhi     ")
city=c("Chennai","Mumbai","Hyderabad","Ahmedabad","Bangalore","Surat","Kolkata","Pune","Delhi")
n=1
print.noquote("   City               Average  Cost For Two in Rs")
print.noquote("             ")
for(i in city){
  x=cost%>%filter(city==i)
  print.noquote(paste(cities[n],"                     ",round(summarise(x," "=mean(costForTwoStrings)))))
  n=n+1
}
```

### 2. Number of Reastaurants in different Cities
```{r}
print.noquote("   City                      Number Of Reastaurants")
print.noquote("             ")
n=1
for(i in city){
  x=cost%>%filter(city==i)%>%group_by(city)
  print.noquote(paste(cities[n],"                       ",nrow(x)))
  n=n+1
}
```


### 3. Types of Cuisenes Available
```{r}
dish=c()
for(i in df$cuisines ){
  a=unlist(strsplit(i,"'"))
  for(j in 1:length(a)){
    if((a[j]!="[") & (a[j]!="]") & (a[j]!=" ")){
      dish=c(dish,noquote(a[j]))
    }
  }
}
print((unique(dish)))
```


### 4. Each Cuisine is Served by how many Reastaurants
```{r}
cbind(table(dish))
```

### 5. Which Cuisine is available Mostly
```{r}
m=max(table(dish))
dish=(sort(table(dish)))
dish[length(dish)]
```

### 6.Swiggy Banglore Analysis
```{r}
blr=read.csv("Swiggy Bangalore Outlet Details.csv")
blr=blr[complete.cases(blr),]


print(paste("Maximum Rated Reastaurant : ",blr$Shop_Name[which(blr$Rating==max(blr$Rating))]))
print.noquote(paste("         Location:             ",blr$Location[which(blr$Rating==max(blr$Rating))]))
print.noquote(paste("         Rating:                     ",blr$Rating[which(blr$Rating==max(blr$Rating))]))
print.noquote(paste("         Average cost for 2:    Rs ",substr(blr$Cost_for_Two[which(blr$Rating==max(blr$Rating))],4,7)))
print.noquote(paste("         Cuisines Available:   ",blr$Cuisine[which(blr$Rating==max(blr$Rating))]))

for(i in 1:4){
  print.noquote("   ")
}

print(paste("Minimum Rated Reastaurant : ",blr$Shop_Name[which(blr$Rating==min(blr$Rating))]))
print.noquote(paste("         Location:             ",blr$Location[which(blr$Rating==min(blr$Rating))]))
print.noquote(paste("         Rating:                     ",blr$Rating[which(blr$Rating==min(blr$Rating))]))
print.noquote(paste("         Average cost for 2:    Rs ",substr(blr$Cost_for_Two[which(blr$Rating==min(blr$Rating))],4,7)))
print.noquote(paste("         Cuisines Available:   ",blr$Cuisine[which(blr$Rating==min(blr$Rating))]))

```

## Data Visualization

### 1.Horizontal Bar Chart  with sums of each rating
```{r}

library(dplyr)
df %>% select(avgRating)%>% group_by(avgRating) %>% count()  %>%
  ggplot(aes(x=reorder(avgRating,n),y=n))+ 
  geom_bar(stat = "identity", fill= "steelblue") + theme_minimal()+
  coord_flip() + geom_text(aes(label=n),vjust=0.3,size=3.5,color="black")
```

### 2. Pie Chart for City wise Distribution on Swiggy

```{r}

pie(table(df$city),main="Citywise distribution")
```
### 3. Bar Plot to visualize the Vegetarian Lovers

```{r}
#Bar Plot to visualize the Vegetarian Lovers
ggplot(df,aes(x=veg,fill=veg))+ geom_bar() + ggtitle("Vegetarian Reastaurant Type") + xlab("Distribution")

```
### 4. 3D pie chart

```{r}

library(plotrix)
#install.packages("plotrix")
x=c(6400,2254)
names(x)=c("Non-Veg","Veg")
pie3D(x ,labels=names(x) ,col = "white",
main = "3D distribution",
labelcol = "darkgreen", col.main = "darkgreen")
```

### 5. histogram Showing Number of deliveries in a paricular time range

```{r}
hist(df$deliveryTime,main="Number of Deliveries in different Time Range",xlab="Time in min")
```

### 6. Box Plot For Summary statistics

```{r}

boxplot(df$maxDeliveryTime)

```

### 7. Density plot for the cities

```{r}


theme_set(theme_classic())

# Plot
g <- ggplot(df, aes(city))
g + geom_density(aes(fill=factor(city)), alpha=0.8) + 
    labs(title="Density plot", 
         subtitle="City grouped by Avg-Rating",
         x="City ",
         fill="# Cities")
```


## Classification Model

```{r}
cost$avgRating=as.numeric(cost$avgRating)
cost$costForTwoStrings=as.numeric(cost$costForTwoStrings)
cost$deliveryTime =as.numeric(cost$deliveryTime)



#is.na(cost$avgRating)
#is.na(cost$costForTwoStrings)
#is.na(cost$deliveryTime)

cost=cost[complete.cases(cost),]
dim(cost)

for (i in colnames(cost)){
  print(sum(is.na(cost[i])))
}

```



### KNN

```{r}

#install.packages("class")
library(class)
library(MASS)

train_set = cost[0:4324,c("costForTwoStrings","deliveryTime","avgRating")]
test_set = cost[4325:5406,c("costForTwoStrings","deliveryTime","avgRating")]


train_scale = scale(train_set[,c("avgRating","costForTwoStrings","deliveryTime")] )
test_scale = scale (test_set[,c("avgRating","costForTwoStrings","deliveryTime")] )

classifier_knn = knn(train = train_scale, test = test_scale, cl = train_set$avgRating, k = 1)
table(classifier_knn)
 
```

```{r}
misClassError = mean(classifier_knn != test_set$avgRating)
per =  round((1-misClassError)*100, 2)
paste0('Accuracy =', per, '%')
```


### GBM

```{r}
#install.packages("gbm")
#install.packages('caret')
library(gbm)


train_set = cost[0:4324,c("costForTwoStrings","deliveryTime","avgRating")]
test_set = cost[4325:5406,c("costForTwoStrings","deliveryTime","avgRating")]

test_x= test_set[,-3]
test_y = test_set[,3]

model_gbm = gbm(train_set$avgRating ~.,data = train_set,distribution = "gaussian",cv.folds = 10,shrinkage = .01,n.minobsinnode = 10,n.trees = 400)
```


```{r}

pred_y=predict.gbm(model_gbm, test_x)
```


```{r}
residuals = test_y - pred_y
RMSE = sqrt(mean(residuals^2))
x=(100.0- round(RMSE,3))
paste("Accuracy :",x)
```



### Decision Tree

```{r}
#install.packages("caTools")
#install.packages("party")
library(datasets)
library(caTools)
library(party)
library(dplyr)
library(magrittr)

copy=cost

copy$city = as.integer(factor(copy$city))
copy$area = as.integer(factor(copy$area))
copy$totalRatingsString = as.integer(factor(copy$totalRatingsString))
copy$veg= as.integer(factor(copy$veg))


str(copy)
```



```{r}
copy=copy[,c("city","area","totalRatingsString","avgRating","veg","deliveryTime")]
copy$avgRating= as.integer(factor(copy$avgRating))

str(copy)


sample_data = sample.split(copy, SplitRatio = 0.8)
train_data <- subset(copy, sample_data == TRUE)
test_data <- subset(copy, sample_data == FALSE)

model<- ctree(avgRating ~ ., train_data)
plot(model)
```

```{r}
test_data$avgRating
```


```{r}
pred = predict(model,test_data,type="prob")
residuals = as.integer(test_data$avgRating) -as.integer(pred)
RMSE = sqrt(mean(residuals^2))
x=(100.0- round(RMSE,3))
paste("Accuracy :",x)
```

```{r}
str(cost)
```


```{r}
library(dplyr)
library(Hmisc)
library(stringr)
#install.packages("svDialogs")
library(svDialogs)

cost$avgRating=as.numeric(cost$avgRating)

one=function(cty,rs,ps){
  for1=as.integer((cost$costForTwoStrings)/2)
  forn=as.integer(ps*for1)
  cost=cbind(cost,forn)
  l=rs-1000
  u=rs+1000
  ans=cost%>%filter(city==cty)%>%filter(forn>=l & u>=forn)%>%subset(select=c("name","avgRating","costForTwoStrings","maxDeliveryTime","cuisines","address","forn","city"))
  maxx=which(ans$avgRating==max(ans$avgRating))
  print(ans[maxx,])
}

two=function(cty,ar){
  ans=cost%>%filter(city==cty)%>%filter(area==ar)%>%subset(select=c("name","avgRating","costForTwoStrings","maxDeliveryTime","cuisines","address","area","city"))
  maxx=which(ans$avgRating==max(ans$avgRating))
  print(ans[maxx,])
}

three=function(cus,tm){
  ans=cost%>%filter(str_detect(cost$cuisines,cus))%>%filter(deliveryTime==tm)%>%subset(select=c("name","avgRating","costForTwoStrings","maxDeliveryTime","cuisines","address","city"))
  maxx=which(ans$avgRating==max(ans$avgRating))
  print(ans)

}

print(noquote("Enter the selection parameter number :"))
print(noquote("1.   by choosing Budget & city"))
print(noquote("2.   by choosing city & area "))
print(noquote("3.   by choosing max delivery time & cuisine"))

#choice = as.integer(readline(prompt = "Enter number : "))

choice=as.numeric(dlgInput("Enter your choice: ", Sys.info()["user"])$res)

if(choice==1){
  city=dlgInput("Enter City: ", Sys.info()["user"])$res
  budget=as.numeric(dlgInput("Enter Budget: ", Sys.info()["user"])$res)
  person=as.numeric(dlgInput("Enter No. of persons : ", Sys.info()["user"])$res)
  one(city,budget,person)
}else if(choice==2){
  city=dlgInput("Enter City: ", Sys.info()["user"])$res
  area=dlgInput("Enter Area: ", Sys.info()["user"])$res
  two(city,area)
}else{
  #cuisine=readline(prompt="Cuisine :")
  #time=readline(prompt="Delivery Time :")
  cuisine=dlgInput("Enter Cuisine: ", Sys.info()["user"])$res
  time=as.numeric(dlgInput("Enter Time: ", Sys.info()["user"])$res)
  three(cuisine,time)
}
```

