---
title: "Zomato Whole"
author: "Team S"
date: "2022-10-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Loading the dataset

```{r}
print(getwd())
df=read.csv(file ="zomato_whole.csv")
```


## Data Structure

```{r}
head(df)
```




```{r}
str(df)
```

```{r}
summary(df)
```

## Data Cleaning and Imputation

### Removing Records having NA values


```{r}
df=df[complete.cases(df),]
dim(df)
```

```{r}
#install.packages("Hmisc")
library(ggplot2)
library(Hmisc)
library(dplyr)
```

```{r}
df$Average_Cost_for_two[is.na(df$Average_Cost_for_two)] <- mean(df$Average_Cost_for_two, na.rm = TRUE) 
```


### Selecting Indian Records
```{r}
df=df%>%filter(Currency=="Indian Rupees(Rs.)")
```

```{r}
avg=df$Average_Cost_for_two
dim(df)
```

## Data Analysis

### 1. Average Cost for 2 in all cities
```{r}
city=unique(df$City)
cities=city
print.noquote("   City                      Average Cost For Two in Rs")
print.noquote("             ")
n=1
for(j in 1:43){
  len=nchar(cities[j])
  len=30-len
  space=""
  for(i in 1:len){
    space=paste(space,"")
  }
  cities[j]=paste( cities[j],space)
}
for(i in city){
  x=filter(df,City==i)
  print.noquote(paste(cities[n]," ",round(mean(x$Average_Cost_for_two))))
  n=n+1
}
```

### 2. Number of Reastaurants in different Cities
```{r}
print.noquote("   City                                   Number Of Reastaurants")
print.noquote("             ")
n=1
for(i in city){
  x=df%>%filter(City==i)%>%group_by(City)
  print.noquote(paste(cities[n],"                       ",nrow(x)))
  n=n+1
}
```


### 3. Types of Cuisenes Available
```{r}
dish=c()
for(i in df$Cuisines ){
  a=unlist(strsplit(i,","))
  for(j in 1:length(a)){
    if((a[j]!="[") & (a[j]!="]") & (a[j]!=" ")){
      dish=c(dish,noquote(a[j]))
    }
  }
}
print((unique(dish)))
```


### 4. Each Cuisine is Served by how many Reastaurants
```{r}
cbind(table(dish))
```

### 5. Which Cuisine is available Mostly
```{r}
m=max(table(dish))
dish=(sort(table(dish)))
dish[length(dish)]
```


### 6. Zomato Banglore Analysis
```{r}
blr=read.csv("zomato.csv")
blr$rate=as.double(substr(as.character(blr$rate),1,3))
blr=blr[complete.cases(blr),1:17]


print(paste("Maximum Rated Reastaurant : ",blr$name[which(blr$rate==max(blr$rate))]))
print.noquote(paste("         Location:             ",blr$location[which(blr$rate==max(blr$rate))]))
print.noquote(paste("         Rating:                     ",blr$rate[which(blr$rate==max(blr$rate))]))
print.noquote(paste("         Average cost for 2:    Rs ",blr$approx_cost[which(blr$rate==max(blr$rate))]))
print.noquote(paste("         Cuisines Available:   ",blr$cuisines[which(blr$rate==max(blr$rate))]))

for(i in 1:4){
  print.noquote("   ")
}

print(paste("Maximum Rated Reastaurant : ",blr$name[which(blr$rate==min(blr$rate))]))
print.noquote(paste("         Location:             ",blr$location[which(blr$rate==min(blr$rate))]))
print.noquote(paste("         Rating:                     ",blr$rate[which(blr$rate==min(blr$rate))]))
print.noquote(paste("         Average cost for 2:    Rs ",blr$approx_cost[which(blr$rate==min(blr$rate))]))
print.noquote(paste("         Cuisines Available:   ",blr$cuisines[which(blr$rate==min(blr$rate))]))

```

```{r}
str(df)
```



## Data Visualization

### 1.Horizontal Bar Chart  with sums of each rating
```{r}
library(dplyr)
df %>% select(Aggregate.rating)%>% group_by(Aggregate.rating) %>% count()  %>%
  ggplot(aes(x=reorder(Aggregate.rating,n),y=n))+ 
  geom_bar(stat = "identity", fill= "steelblue") + theme_minimal()+
  coord_flip() + geom_text(aes(label=n),vjust=0.3,size=3.5,color="black")
```

### 2. Pie Chart for City wise Distribution on Swiggy

```{r}

pie(table(df$City),main="Citywise distribution")
```

### 3. Box Plot For Summary statistics

```{r}

boxplot(df$Votes)

```

### 4. Density plot for the cities

```{r}


theme_set(theme_classic())

# Plot
g <- ggplot(df, aes(City))
g + geom_density(aes(fill=factor(City)), alpha=0.8) + 
    labs(title="Density plot", 
         subtitle="City grouped by Avg-Rating",
         x="City ",
         fill="# Cities")
```

```{r}
str(df)
```

```{r}
8652*0.80


#df$City=as.numeric(factor(df$City))
df$Rating.text=as.numeric(factor(df$Rating.text))


```
### KNN

```{r}
#install.packages("class")
library(class)
library(MASS)


train_set = df[0:6921  ,c("Price.range","Votes","Aggregate.rating")]
test_set = df[6922:8652,c("Price.range","Votes","Aggregate.rating")]


#train_scale = scale(train_set[,c("Price.range","Votes","Average_df_for_two","Aggregate.rating")] )
#test_scale = scale (test_set[,c("Price.range","Votes","Average_df_for_two","Aggregate.rating")] )

classifier_knn = knn(train = train_set, test = test_set, cl = train_set$Aggregate.rating, k = 1)
table(classifier_knn)
```


```{r}
misClassError = mean(classifier_knn != test_set$Aggregate.rating)
per =  round((1-misClassError)*100, 2)
paste('Accuracy = ', per, '%')
```


### Decision Tree
```{r}
#install.packages("caTools")
#install.packages("party")
library(datasets)
library(caTools)
library(party)
library(dplyr)
library(magrittr)

copy=df[,c("Price.range","Votes","Aggregate.rating")]
copy$Aggregate.rating= as.integer(factor(df$Aggregate.rating))


sample_data = sample.split(copy, SplitRatio = 0.8)
train_data <- subset(copy, sample_data == TRUE)
test_data <- subset(copy, sample_data == FALSE)

model<- ctree(Aggregate.rating ~ ., train_data)
plot(model)
```

```{r}
pred = predict(model,test_data,type="prob")
residuals = as.integer(test_data$Aggregate.rating) -as.integer(pred)
RMSE = sqrt(mean(residuals^2))
x=(100.0- round(RMSE,3))
paste("Accuracy :",x)
```



###  GBM

```{r}
#install.packages("gbm")
#install.packages('caret')
library(gbm)


train_set = df[0:6921  ,c("Price.range","Votes","Aggregate.rating")]
test_set = df[6922:8652,c("Price.range","Votes","Aggregate.rating")]

test_x= test_set[,-3]
test_y = test_set[,3]

model_gbm = gbm(train_set$Aggregate.rating ~.,data = train_set,distribution = "gaussian",cv.folds = 10,shrinkage = .01,n.minobsinnode = 10,n.trees = 10)
```

```{r}
pred_y=predict.gbm(model_gbm, test_x)
pred_y=round(pred_y,2)
```

```{r}
residuals =  pred_y-test_y
RMSE = sqrt(mean(residuals^2))
x=(100.0- round(RMSE,3))
paste("Accuracy :",x)
```

```{r}
tail(df)
```

```{r}
library(dplyr)
library(Hmisc)
library(stringr)
#install.packages("svDialogs")
library(svDialogs)


df$Average_Cost_for_two=avg
df$Aggregate.rating=as.numeric(df$Aggregate.rating)

one=function(cty,rs,ps){
  for1=as.numeric((df$Average_Cost_for_two)/2)
  forn=as.numeric(ps*for1)
  df=cbind(df,forn)
  l=rs-3000
  u=rs+3000
  ans=df%>%filter(City==cty)%>%filter(forn>=l & u>=forn)%>%subset(select=c("Restaurant.Name","Aggregate.rating","Average_Cost_for_two","Cuisines","Votes","Address","forn","City"))
  maxx=which(ans$Aggregate.rating==max(ans$Aggregate.rating))
  print(ans[maxx,])
}

two=function(cty,ar){
  ans=df%>%filter(City==cty)%>%filter(area==ar)%>%subset(select=c("Restaurant.Name","Aggregate.rating","Average_Cost_for_two","Cuisines","Address","City"))
  maxx=which(ans$Aggregate.rating==max(ans$Aggregate.rating))
  print(ans[maxx,])
}

three=function(cus){
  ans=df%>%filter(str_detect(df$Cuisines,cus))%>%subset(select=c("Restaurant.Name","Aggregate.rating","Average_Cost_for_two","Cuisines","Address","City"))
  maxx=which(ans$Aggregate.rating==max(ans$Aggregate.rating))
  print(ans[maxx,])

}

print(noquote("Enter the selection parameter number :"))
print(noquote("1.   by choosing Budget & city"))
print(noquote("2.   by choosing city & area "))
print(noquote("3.   by choosing max delivery time & cuisine"))

#choice = as.integer(readline(prompt = "Enter number : "))

choice=as.numeric(dlgInput("Enter your choice: ", Sys.info()["user"])$res)

if(choice==1){
  city=dlgInput("Enter City: ", Sys.info()["user"])$res
  budget=as.numeric(dlgInput("Enter Budget: ", Sys.info()["user"])$res)
  person=as.numeric(dlgInput("Enter No. of persons : ", Sys.info()["user"])$res)                                         #Agra 2000 4
  one(city,budget,person)
}else if(choice==2){
  city=dlgInput("Enter City: ", Sys.info()["user"])$res                                                                     # Vizag  Siripuram
  area=dlgInput("Enter Area: ", Sys.info()["user"])$res
  two(city,area)
}else{
  #cuisine=readline(prompt="Cuisine :")
  #time=readline(prompt="Delivery Time :")
  cuisine=dlgInput("Enter Cuisine: ", Sys.info()["user"])$res                                                  # Rajasthani
  #time=(dlgInput("Deliver Online : ", Sys.info()["user"])$res)
  three(cuisine)
}
```
